---
title: "Report Analysis"
output: html_notebook
date: "01/16/2023"
by: Khadijat I.
---

This is the report for the analysis of the data "REPORT_TO_ANALYZE".

#PREPARING DATA  
The titles of the columns where made consistent within excel spreadsheet and imported to RStudio where the analysis took place.

#DATA WRANGLING  
While cleaning the data to remove the character included withing the columns, the data rendered NA.

```{r}
report_to_analyze$country <- gsub("_","",as.numeric(report_to_analyze$country))
report_to_analyze$gender <- gsub("_","",as.integer(report_to_analyze$gender))
report_to_analyze$age_ranges <- gsub("_","",as.integer(report_to_analyze$age_ranges))
report_to_analyze$occupation_screener <- gsub("_","",as.integer(report_to_analyze$occupation_screener))
report_to_analyze$frequency <- gsub("_","",as.integer(report_to_analyze$frequency))
report_to_analyze$attitudes <- gsub("_","",as.integer(report_to_analyze$attitudes))
report_to_analyze$destination <- gsub("_","",as.numeric(report_to_analyze$destination))
report_to_analyze$departure_us <- gsub("_","",as.numeric(report_to_analyze$departure_us))
report_to_analyze$quotas_departure_us <- gsub("_","",as.numeric(report_to_analyze$quotas_departure_us))
report_to_analyze$lifestage <- gsub("_","",as.numeric(report_to_analyze$lifestage))
report_to_analyze$how_do_you_travel <- gsub("_","",as.numeric(report_to_analyze$how_do_you_travel))
report_to_analyze$time_last_flight <- gsub("_","",as.numeric(report_to_analyze$time_last_flight))
report_to_analyze$excited_towards_next_flight <- gsub("_","",as.numeric(report_to_analyze$excited_towards_next_flight))
```


```{r}
head(report_to_analyze)
```


#DATA ANALYSIS  
  
Only three columns are available for analysis:  
  
* exact_age
* share_leisure
* share_business  
  
Each of the columns are analysed for:  
  
* mean
* standard deviatio
* correlation between the variables
* plot showing relationship between the variables  

```{r}
report1 <- 
  report_to_analyze %>%
  summarise(mean(exact_age), sd(exact_age), mean(share_leisure),
            sd(share_leisure), mean(share_business), sd(share_business),
            cor(share_business, exact_age, method = "pearson"),
            cor(share_leisure, exact_age, method = "pearson"),
            .groups = NULL)
```


```{r}
View(report1)
```


```{r}
head(report1)
```


```{r}
ggplot(report_to_analyze)+
  geom_line(mapping = aes(x=report_to_analyze$exact_age,y=report_to_analyze$share_business))
```


```{r}
ggplot(report_to_analyze)+
  geom_line(mapping = aes(x=report_to_analyze$share_leisure,y=report_to_analyze$share_business))
```

```{r}
ggplot(report_to_analyze)+
  geom_line(mapping = aes(x=report_to_analyze$exact_age,y=report_to_analyze$share_leisure))
```

Linear regression by Pearson for the variables that are related. The share_business and share_leisure.

```{r}
lm(report_to_analyze$share_leisure~report_to_analyze$share_business)
```
